### 2017-07-29 README.Rmd
remove warnings about fluctuation failures

`drtmle` is an R package that computes marginal effect estimators for binary 
treatments on continuous and binary outcomes. The targeted minimum loss-based (TMLE) estimators are doubly robust, not only with respect to consistency, but also with respect to asymptotic normality, as discussed in Benkeser, Carone, van der Laan \& Gilbert, 2017,(_accepted Biometrika_, [working paper](http://biostats.bepress.com/ucbbiostat/paper356/)). Therefore, it is possible to construct doubly-robust confidence intervals and hypothesis tests. Also included are methods for computing valid confidence intervals for an inverse probability of treatment weighted (IPTW) estimator of the average treatment effect when the propensity score is estimated via super learning, as discussed in [van der Laan, 2014](https://www.degruyter.com/downloadpdf/j/ijb.2014.10.issue-1/ijb-2012-0038/ijb-2012-0038.pdf).

>>>>

`drtmle` is an R package that computes marginal effect estimators for binary 
treatments on continuous and binary outcomes. The targeted minimum loss-based (TMLE) estimators are doubly robust, not only with respect to consistency, but also with respect to asymptotic normality, as discussed in Benkeser, Carone, van der Laan \& Gilbert, 2017 (_accepted Biometrika_; [working paper](http://biostats.bepress.com/ucbbiostat/paper356/)). Therefore, it is possible to construct doubly-robust confidence intervals and hypothesis tests. Also included are methods for computing valid confidence intervals for an inverse probability of treatment weighted (IPTW) estimator of the average treatment effect when the propensity score is estimated via super learning, as discussed in [van der Laan, 2014](https://www.degruyter.com/downloadpdf/j/ijb.2014.10.issue-1/ijb-2012-0038/ijb-2012-0038.pdf).
